Response to the defense feedback

### 2021-06-19 Chapter-4/Chapter-4.tex
Updates from Overleaf

    \subfloat[OpenSSL 1.1.0f]{
        \includegraphics[width=.3\linewidth]{./figures/chapter4/result/RSA-openssl-1-1-0f.pdf}
        \label{fig:rsa-4}
    }
    \subfloat[OpenSSL 1.1.1]{
        \includegraphics[width=.3\linewidth]{./figures/chapter4/result/RSA-openssl-1-1-1.pdf}
        \label{fig:rsa-5}
    }
    \subfloat[OpenSSL 1.1.1g]{
        \includegraphics[width=.3\linewidth]{./figures/chapter4/result/RSA-openssl-1-1-1g.pdf}
        \label{fig:rsa-6}
    }
    \caption{Side-channel leakages in different implementations of RSA in OpenSSL\@. 
        We round the number of leaked information into the nearest integer. 
        The mark $*$ means timeout.}
    \label{fig:rsa}
\end{figure*}
We also evaluate \tool{} on RSA.  %, which is available online at the tool release website.
%% \jl{where?}. In general,
%% developers are interested in fixing side-channel vulnerabilities for the RSA implementations.
%% \jl{Then maybe find some space to present these results?}
 As shown in Figure~\ref{fig:rsa}, the result indicates that the newer
versions of OpenSSL leak less information than the earlier
versions. After version 0.9.7g, OpenSSL adopts a fixed-window \textsf{mod\_exp\_mont}
implementation for RSA\@. With this design, the sequence of squares and
multiples and the memory access patterns are independent of the secret key.
\tool{}'s result confirms the new exponentiation implementation has mitigated 
most leakages effectively because the four newer versions have fewer
leakages than version 0.9.7, which introduced this change.
OpenSSL version 1.0.2f, 1.0.2k, and 1.1.0f almost have the
same amount of leakage. We check the ChangeLog and find only one change to
patch vulnerability CVE-2016-0702. 
\tool{} finds OpenSSL 1.1.1 and 1.1.1g have significantly less
leaked information than other versions.
We check the ChangeLog of these two versions and find a claim that
the new RSA implementation adopts ``numerous side-channel attack mitigation'', 
which proves the effectiveness of our quantifying method.
%We also observe the latest version (1.1.1g) contains some new leakages. We have
%contacted the developers and they have confirmed our findings.

@@

For vulnerabilities that leak less amount of information,
developers are more reluctant to fix them or fixing them unintentionally. For example, OpenSSL 0.9.7 adds a fixed windows version of function \textsf{BN\_mod\_exp\_mont\_consttime} to replace original function \textsf{BN\_mod\_exp\_mont}.
\tool{} detects a minor vulnerability in the original function that can leak the last bit of the big number \texttt{m}. In the updated version, developers make the fixed windows the default option and rewrite most of the function. However, the leakage site still exists in OpenSSL 1.1.1.
\begin{figure}
    \centering
    \begin{lstlisting}[xleftmargin=.08\textwidth, xrightmargin=.0\textwidth, frame=none]
# define mul_add_c2(a,b,c0,c1,c2)                    \
    t=(BN_ULLONG)a*b;                                \
    tt=(t+t)&BN_MASK;                                \
    if (tt < t) c2++;                                \
    t1=(BN_ULONG)Lw(tt);                             \
    t2=(BN_ULONG)Hw(tt);                             \
    c0=(c0+t1)&BN_MASK2;                             \
    if ((c0 < t1) && (((++t2)&BN_MASK2) == 0)) c2++; \
    c1=(c1+t2)&BN_MASK2; if ((c1) < t2) c2++;
\end{lstlisting}
    \caption{Macro \textsf{sqr\_add\_c2} in OpenSSL 0.9.7}
    \label{fig:old_sqr2}
\end{figure}

>>>>

    \subfloat[OpenSSL 1.1.0f]{
        \includegraphics[width=.3\linewidth]{./figures/chapter4/result/RSA-openssl-1-1-0f.pdf}
        \label{fig:rsa-4}
    }
    \subfloat[OpenSSL 1.1.1]{
        \includegraphics[width=.3\linewidth]{./figures/chapter4/result/RSA-openssl-1-1-1.pdf}
        \label{fig:rsa-5}
    }
    \subfloat[OpenSSL 1.1.1g]{
        \includegraphics[width=.3\linewidth]{./figures/chapter4/result/RSA-openssl-1-1-1g.pdf}
        \label{fig:rsa-6}
    }
    \caption{Side-channel leakages in different implementations of RSA in OpenSSL\@. 
        We round the number of leaked information into the nearest integer. 
        The mark $*$ means timeout.}
    \label{fig:rsa}
\end{figure*}
We also evaluate \tool{} on RSA.  %, which is available online at the tool release website.
%% \jl{where?}. In general,
%% developers are interested in fixing side-channel vulnerabilities for the RSA implementations.
%% \jl{Then maybe find some space to present these results?}
 As shown in Figure~\ref{fig:rsa}, the result indicates that the newer
versions of OpenSSL leak less information than the earlier
versions. After version 0.9.7g, OpenSSL adopts a fixed-window \textsf{mod\_exp\_mont}
implementation for RSA\@. With this design, the sequence of squares and
multiples and the memory access patterns are independent of the secret key.
\tool{}'s result confirms the new exponentiation implementation has mitigated 
most leakages effectively because the four newer versions have fewer
leakages than version 0.9.7.
OpenSSL version 1.0.2f, 1.0.2k, and 1.1.0f almost have the
same amount of leakage. We check the ChangeLog and find only one change to
patch vulnerability CVE-2016-0702. 
\tool{} finds OpenSSL 1.1.1 and 1.1.1g have significantly less
leaked information than other versions.
We check the ChangeLog of these two versions and find a claim that
the new RSA implementation adopts ``numerous side-channel attack mitigation'', 
which proves the effectiveness of our quantifying method.
%We also observe the latest version (1.1.1g) contains some new leakages. We have
%contacted the developers and they have confirmed our findings.

@@

For vulnerabilities that leak less amount of information,
developers are more reluctant to fix them or fixing them unintentionally. For example, OpenSSL 0.9.7 adds a fixed windows version of function \textsf{BN\_mod\_exp\_mont\_consttime} to replace the original function \textsf{BN\_mod\_exp\_mont}.
\tool{} detects a minor vulnerability in the original function that can leak the last bit of the big number \texttt{m}. In the updated version, developers make the fixed windows the default option and rewrite most of the function. However, the leakage site still exists in OpenSSL 1.1.1.
\begin{figure}
    \centering
    \begin{lstlisting}[xleftmargin=.08\textwidth, xrightmargin=.0\textwidth, frame=none]
# define mul_add_c2(a,b,c0,c1,c2)                    \
    t=(BN_ULLONG)a*b;                                \
    tt=(t+t)&BN_MASK;                                \
    if (tt < t) c2++;                                \
    t1=(BN_ULONG)Lw(tt);                             \
    t2=(BN_ULONG)Hw(tt);                             \
    c0=(c0+t1)&BN_MASK2;                             \
    if ((c0 < t1) && (((++t2)&BN_MASK2) == 0)) c2++; \
    c1=(c1+t2)&BN_MASK2; if ((c1) < t2) c2++;
\end{lstlisting}
    \caption{Macro \textsf{sqr\_add\_c2} in OpenSSL 0.9.7}
    \label{fig:old_sqr2}
\end{figure}
